Are we learning to build better models at the cost of better decisions?

### 2021-03-18 manuscript/manuscript.Rmd
:pen: drafting intro

<!-- Open on real-world issues, uncertainty, particularly model uncertainty as key theme.  -->

Global change issues are complex and outcomes are difficult to predict, making approaches to uncertainty a central part
of effective decision-making [@ @]. Reducing that uncertainty through additional data collection and evaluation of outcomes
is essential for effective management [@].

@@

[^1]: While some authors distinguish between model uncertainty and parameter uncertainty, I will refer collectively to
any uncertainty that arises from our imperfect knowledge of the system as "model uncertainty". Uncertainty in model structure can often be reflected by appropriate parameterization, just as models with different parameter values can be treated distinctly. Whereas stochasticity is inherent to the process (or rather, to our choice of state variables, @Boettiger2018) and measurement uncertainty can only be reduced by more accurate tools for measurement, model uncertainty is reducible by learning from additional data.

>>>>

<!-- Open on real-world issues, uncertainty, particularly model uncertainty as key theme.  -->
Global change issues are complex and outcomes are difficult to predict  [@Clark2001]. 
To guide decisions in an uncertainty world, researchers and decision makers 
may consider a range of alternative plausible models[^1] to better reflect 
what we do and do not know about the processes involved [@Polasky2011].  Forecasts or
predictions from possible models can indicate what outcomes are most likely to result
under what decisions or actions.  Further, by comparing the outcomes predicted by a model
to future observations, a decision maker can not only _plan_ for the uncertainty, but 
also _learn_ which models are most trustworthy.  This iterative learning process is
particularly appealing because the models which best fit currently available data are not 
always the models which lead to the best decisions.  Such outcomes are often characterized
as the result of "over-fitting" [@Burnham2002]. While many methods (e.g. information criteria @Burnham2002)
are developed seeking to avoid this

While models
may also reflect uncertainties intrinsic to the process (stochasticity) or the limits 
of measurement (observation uncertainty),

Why then do some models which most closely match available data lead to worse outcomes than models which appear less accurate?
This situation is almost universally considered to be the result of "over-fitting" [@], which much effort is dedicated to avoiding 
in selecting models. Because the defining flaw of an over-fit model is the failure to correctly predict additional data,

<!-- even in a world absent of power politics, conflicting incentives, imperfect implementation, this is not an issue that can be addressed by statistics and data alone.  The

making approaches to uncertainty a central part
of effective decision-making [@Polasky2011; @Clark2001]. Reducing that uncertainty through additional data collection 
and evaluation of outcomes is thus essential for effective management [@walters1978].

@@

[^1]: While some authors distinguish between model uncertainty and parameter uncertainty, I will refer collectively to
any uncertainty that arises from our imperfect knowledge of the system as "model uncertainty," because the distinction
is largely a consequence of notation rather something more intrinsic.  For example, two structurally different models, $f(x) = a x$
and $f(x) = a x^2$ can be considered merely different parameterizations of $f(x) = a x^b$, or vice versa.
